Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-14 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Updated the cited papers

Nevertheless, there are challenges when using MIM tools that occur due to the blurring of boundaries between academic and private life. This can lead to technostress \cite{gachago2015crossing}, difficulty in managing responsibilities especially among mature students and lack of privacy \cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students (Abbas et al., 2021b) % This one is missing from the biblio
without affecting students' ownership and control that is vital to advance their learning \cite{gachago2015crossing}.

% The Use of Chatbots in Higher Education
The use of conversational agents or chatbots in higher education is still at its infancy cite{yang2019opportunities}. Nevertheless, recent studies examining their positive impact on students' academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes. Indeed, the use of chatbots in collecting course feedback from students in higher education improved students' response quality and boosted their enjoyment levels (Abbas, Pickard, Atwell and Walker, 2021a).  According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation. In this sense, \cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning.

Several higher education chatbots' evaluation studies were undertaken. For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform. Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented \cite{perez2020rediscovering}. The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) % We probably need a reference for this - JJ
and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
) answers students' frequently asked questions about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.  \cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions; for some time, the University of Granada had ELVIRA as a chatbot in their main page \cite{MOREO20129}. Besides being able to answer pre-established (frequent) questions, it did so from the main University of Granada using an inset character, voiced by a real person, who lip-synched the answers. The emphasis in this case, however, was on the authenticity of the synchronization more than in making the update of questions and answers simpler, or more interactive, using actual messaging platforms. In most cases, using the inset search engine was able to give you more up-to-date and accurate answers.

>>>>

Nevertheless, there are challenges when using MIM tools that occur due to the blurring of boundaries between academic and private life. This can lead to technostress \cite{gachago2015crossing}, difficulty in managing responsibilities especially among mature students and lack of privacy \cite{tang2017mobile}.  Students' dropout of the MIM groups, as they can leave groups at any time can hinder their learning and undermine educators' efforts \cite{mwakapina2016whatsapp}.  In addition, there is a need to set rules and norms for these MIM groups in order to maintain the safety of these online communities for students \cite{abbas2021onlinechat} without affecting students' ownership and control that is vital to advance their learning \cite{gachago2015crossing}.

% The Use of Chatbots in Higher Education
The use of conversational agents or chatbots in higher education is still at its infancy \cite{yang2019opportunities}. Nevertheless, recent studies examining their positive impact on students' academic performance \cite{perez2020rediscovering} and engagement \cite{differ.chat}(Abbas et al., 2021b) have led to a growing interest in using this technology in classes. Indeed, the use of chatbots in collecting course feedback from students in higher education improved students' response quality and boosted their enjoyment levels \cite{abbas2021Surveys}.  According to \cite{Roblyer2010}, using either tools such as mobile devices or teaching strategies based on gamification \cite{Yildirim2017} can improve student motivation. In this sense, \cite{Pimmer2019} carried out a series of experiments with technological tools whose results showed positive perception and acceptance of the use of technology in teaching and learning.

Several higher education chatbots' evaluation studies were undertaken. For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform. Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented \cite{perez2020rediscovering}. The first category includes those that provide service support such as the chatbot Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration. Ask L.U. \cite{LancasterUniversity_2019} answers students' frequently asked questions about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot} and Differ \cite{differchat} facilitate breaking the ice between new students by introducing them to each other.  \cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions; for some time, the University of Granada had ELVIRA as a chatbot in their main page \cite{MOREO20129}. Besides being able to answer pre-established (frequent) questions, it did so from the main University of Granada using an inset character, voiced by a real person, who lip-synched the answers. The emphasis in this case, however, was on the authenticity of the synchronization more than in making the update of questions and answers simpler, or more interactive, using actual messaging platforms. In most cases, using the inset search engine was able to give you more up-to-date and accurate answers.
